False Positive Probabilities for all Kepler Objects of Interest: \\ \nvalnew\ newly validated planets and \nfpnew\ likely false positives

### 2015-08-24 ms.tex
FP section edits

@@

\begin{figure*}[p]
\begin{center}
\includegraphics[width=7in]{figures/fpp_summary_all.pdf}
\end{center}
\caption{False positive probabilities of all KOIs for which we
  consider the \vespa\ calculations to be reliable.  This includes
  KOIs that are not dispositioned as FALSE POSITIVE on the NExScI
  archive, are considered to be reliably located on the target star ($
  {\rm Pr} > 0.99$) according to pixel-level analysis
  \citep{Bryson:2015}, and for which $\mathcal L_{\rm tot} > 10^{-3}$,
  indicating that the hypotheses tested by \vespa\ are not all poor
  explanations of the data.  Of these \nreliable\ KOIs, \nval\ have
  FPPs less than 1\%.  Noteably, \nreliableFP\ are likely false
  positives (FPP $> 0.5$), consistent with the \citet{Morton:2011} and
  \citet{Fressin:2013} \emph{a priori} estimates of the overall
  \kepler\ candidate false positive rate.

\figlabel{fppall}}
\end{figure*}

>>>>

In order to properly interpret these results, it is necessary to
understand the range of applicability of the \vespa\ calculation.
First of all, this method selects between different \emph{eclipse
  configuration} explanations for the transit-like signal, and cannot
comment on whether the signal might be caused by stellar variability
or an instrumental false alarm.  Thus, \vespa\ results on low
signal-to-noise candidates where it is not clear whether the
identified signal is truly transit-like or not must be viewed with
caution.

Another important constraint used in the FPP calculation is the
allowed sky area inside which a blended false positive may live.  As
described in \sect{data}, this value is taken to be three times the
uncertainty on the fitted centroid position from the pixel-level data.
However, many KOIs have already been identified to be blended binaries
displaced from the target star.  Some of these are found by detecting
significant centroid offsets---in these cases, treating the confusion
radius simply as the uncertainty in the centroid position will clearly
give a misleading result.  Other displaced false positives have been
identified as originating from displaced stars by finding KOIs with
matching ephemerides \citep{Coughlin:2014}, and often the ``parents''
of these signals are outside the pixel masks, and so unable to be
detected via the normal centroid-measuring methods.

Thus there are many KOIs that have
already been identified as false alarms (and thus dispositioned FALSE
POSITIVE at the NExScI archive) for which \vespa\ gives a low false
positive probability---all this means is that the planet scenario for
those KOIs is \emph{more} probable than the other scenarios being
considered, but

from several pixels or more away, often the result of
the point spread function (PSF) of a bright eclipsing binary star
leaking into the aperture of a nearby target star
\citep{Coughlin:2014}.  Most of these have been

the limits of the \vespa\ method.

@@

\begin{figure*}[p]
\begin{center}
\includegraphics[width=7in]{figures/fpp_summary_all.pdf}
\end{center}
\caption{False positive probabilities of all KOIs for which we
  consider the \vespa\ calculations to be reliable (floored at
  $10^{-4}$ for visualization purposes).  This includes
  KOIs that are not dispositioned as FALSE POSITIVE on the NExScI
  archive, are considered to be reliably located on the target star ($
  {\rm Pr} > 0.99$) according to pixel-level analysis
  \citep{Bryson:2015}, and for which $\mathcal L_{\rm tot} > 10^{-3}$,
  indicating that the hypotheses tested by \vespa\ are not all poor
  explanations of the data.  Of these \nreliable\ KOIs, \nval\ have
  FPPs less than 1\%.  Noteably, \nreliableFP\ are likely false
  positives (FPP $> 0.5$), consistent with the \citet{Morton:2011} and
  \citet{Fressin:2013} \emph{a priori} estimates of the overall
  \kepler\ candidate false positive rate.
\figlabel{fppall}}
\end{figure*}
